Figures to insert in text

### 2018-04-04 kanerva-answer.tex
teorema 2

Theorem \ref{T1} is valid for both ``x written at x'' (autoassociative memory) and ``random written at x'' (heteroassociative memory). When $n=1,000$ and $r=451$, $P(x_i = y_i | d(x, y) \le r) = p = 0.552905498137$.  Each bit of a hard location does indeed have a small pull bias.  What is meant by this is that each particular dimension has a small preference toward positive values if its address bit is set to 1, and negative values otherwise.

@@

Let $Z$ be the number of activated hard locations with the same bit as the reading address:

$Z = \sum_{i=1}^{h} X_i$,

where $\mathbf{E}[h] = h$, \\
$\mathbf{V}[h] = H p_1 (1-p_1)$, \\
$p_1 = 2^{-n} \sum_{k=0}^{r} \binom{n}{k}$, and \\
$X_i \sim \text{Bernoulli}(p)$. \\

>>>>

Theorem \ref{T1} is valid for both ``x written at x'' (autoassociative memory) and ``random written at x'' (heteroassociative memory). When $n=1,000$ and $r=451$, $P(x_i = y_i | d(x, y) \le r) = p = 0.552905498137$.  Each bit of a hard location does indeed have a small pull bias.  What is meant by this is that each particular dimension has a small preference toward positive values if its address bit is set to 1, and negative values if set to 0.

@@

\begin{proof}
Let $Z$ be the number of activated hard locations with the same bit as the reading address:
$Z = \sum_{i=1}^{h} X_i$,

where $\mathbf{E}[h] = h$, $\mathbf{V}[h] = H p_1 (1-p_1)$, $p_1 = 2^{-n} \sum_{k=0}^{r} \binom{n}{k}$, and $X_i \sim \text{Bernoulli}(p)$.
